Transcriptomic Analysis of Expressions of Biomarkers and Their Prognostic Value in Head and Neck Squamous Cell Carcinoma

### 2021-06-19 Cover_letter_JPM.tex
Updates from Overleaf

% strategy should changing; run GCP Rstudio 框列更多的 candidates for GEO (GSE65858) during candidate selection
In the independent test, half genes have p-values less than 0.05, and most of them have p-values $> 0.01$. % table 1 => this is Bonferroni 的結果
Purely based on the number of genes and their p-values, the validation rate is relatively low, and the usability of the biomarkers is questionable. % the validation rate 
The p-values are affected by the sample size, which should be described in the main text. % writing
As I mentioned above, the authors should look for more data to verify these biomarkers. % GEO GSE65858(ok) or even GSE117973?

@@

% the validation rate
% more GSE datasets; pick-up more candidate (run GCP) in hands 而且要偷看答案
% x using  receiver operating characteristic (ROC) analysis and more GEO datasets
We appreciate the reviewer for the critical comments and thanks for the guidance of our work in cancer research.

%***調整 workflow 更加嚴格以增加 validation rate
%Validation rate:\\
%重新挑選 candidate (FDR100) 多選一些、偷偷看答案(GSE2837 and GSE65858)
% => answer is: consensus top3 genes

% (ok) Table 1/2 caption, Fig KP plot: FDR P value (要改為真的FDR) [line 196]

% [2021/06/11]決議;
We have introduced an independent HNSCC cohort (GSE65858, with RNA-Seq expression data) for helping in candidate selection.
%We further
%validate them by using a independent HNSCC cohort (GSE65858, with RNA-Seq expression data)

% problem of it (少 n=30, and RFS only: validation rate 14/100 而且 10% cutoff)
%x Prognoscan (GSE2837) (n=30 less)  RFS only:  10\% cutoff to yield a \textit{P}-value < 0.05.\\
%找出  3 candidates
Even the top 20 genes listed
%six overexpressed genes (symbol as CAMK2N1, PGK1, SURF4, USP10, NDFIP1, FOXA2) are bad guy;
%four overexpressed genes (symbol as IL19, FCGBP, IQCN - former symbol as KIAA1683, and NPB) are good guy.
%}
in Figure \ref{fig:hazards3}, have significant FDR-adjusted \textit{P} values in Kaplan-Meier estimate, and survival impact on HR ($> 1.8$ or $< 0.6$) in Cox's model. 
%Rplot_GSE65858_CoxHR_CAMK2N1_top3FDRKM.pdf % FDR KM p value of hazards534
% by Validation_GSE65858_survival.R
% Rplot_GSE65858_CoxHR_CAMK2N1_validated.pdf
\begin{figure}
    \centering
    \includegraphics[width=13cm]{Rplot_TCGA_HNSCC_CoxHR_CAMK2N1_top3FDRKM.pdf}
    \bcaption{Volcano plot of genes under survival analyses of TCGA HNSCC.}{
%X axis: unadjusted \textit{P} value of Kaplan-Meier survival (-log10 transformed).
%Y axis: multivariate hazard ratio from Cox proportional regression model.
%Dotted line: significant Bonferroni corrected \textit{P} value. 
%\textcolor{red}{Red dots} mark 10 genes (unvalidated), which impact on poor prognosis ($HR>=1.5$). \textcolor{green}{Green dots} mark 10 genes (unvalidated), which affect on better survival ($HR<=0.5$).
    This cohort has been applied for exploration of the candidate biomarkers.
    Total 9416 genes has \acrshort{fdr}-adjusted \textit{P} value less than 0.05.
    \textcolor{red}{CAMK2N1}, \textcolor{red}{IL19}, \textcolor{red}{FCGBP} and the other 17 genes (marked in \textcolor{black}{black square}) have hazard ratio (HR) $> 1.8$ or $< 0.6$.\\
    Remarks:\\
    \textcolor{red}{Red spots}: $HR > 1.0$;
    \textcolor{green}{Green spots}: $HR < 1.0$;\\
    X-axis: Kaplan-Meier survival estimates, with \acrshort{fdr}-adjusted \textit{P} value (log10 transformed);\\
    Y-axis: HR of Cox proportional hazard regression model\\
    }
    \label{fig:hazards3}
\end{figure}

% [2021/06/13-17]
%CAMK2N1, IL19, and FCGBP is validated by
%candidate_fdr100
%PvalueTex consensus with GSE2837 to yield 3 candidates
In GSE65858 cohorts, CAMK2N1, IL19, and FCGBP, have FDR-corrected \textit{P} value ($< 0.05$), and Cox'HR ($>1.8$ or $<0.65$) (please see Table \ref{tab:table_top3_GSE65858} listed below,
% (ok) (FDR KM \textit{P} value) <= # only MSMB KM FDR-adjusted P value = 0.002 
% Consensus 3 genes in Kaplan-Meier survival and Cox's model (dataset: GSE65858)
%Gene.Symbol KM.Pvalue   FDR.KMpvalue    uni_HR  FDR.Pvalue(in TCGA)
%CAMK2N1 0.00687 0.03782500  1.814   1.628308e-05
%FCGBP   0.01020 0.03886709  0.573   4.827833e-05
%IL19    0.03390   0.04738901    0.630   6.543871e-06
%IL19    0.00269  0.03068073 0.630  6.543871e-06
%candidate_fdr100
and also see Figure \ref{fig:hazards534}), however, the "rank" of other 17 genes are replaced by genes such as DUSP6, MSMB, and RBM11.
In the consensus of TCGA and GSE65858 cohorts, we suggest that CAMK2N1, IL19, and FCGBP are still significant candidates.

% Please add the following required packages to your document preamble:
% \usepackage{graphicx}
\begin{table}[ht]
\centering
\caption{GSE65858 and TCGA Consensus genes in Kaplan-Meier survival and Cox's model}
\label{tab:table_top3_GSE65858}
\resizebox{\linewidth}{!}{%
\begin{tabular}{llll}
Gene Symbol & KM \textit{P} value & FDR-adjusted \textit{P} value & Cox’s univariate HR \\
\hline
CAMK2N1 & \num{6.87e-3} & 0.038 & 1.814 \\
FCGBP   & 0.01 & 0.039 & 0.573 \\
IL19    & 0.03 & 0.047 & 0.63  \\
IL19    & \num{2.69e-3} & 0.031 & 0.63\\
\hline
(values shown in dataset: GSE65858)\\
(IL19 has two probes in RNA-Seq experiment)\\
\hline
\end{tabular}%
}
\end{table}

@@

\begin{figure}
    \centering
    \includegraphics[width=13cm]{Rplot_GSE65858_CoxHR_CAMK2N1_top3FDRKM.pdf}
    \bcaption{Volcano plot of genes under survival analyses of GSE65858 cohort}{
    This HNSCC cohort has been applied for filtering of our candidate genes: "CAMK2N1", "IL19" (two probes), and "FCGBP".
    There are 270 HNSCC participants involved in this cohort.
    The number of genes (or probes of RNA-Seq in platform GPL10558, Illumina HumanHT-12 V4.0 expression beadchip) is 30330.
    Total 534 genes has \acrshort{fdr}-adjusted \textit{P} value less than 0.05
    (\textcolor{red}{Red spots}: hazard ratio is greater than 1.0;
    \textcolor{green}{Green spots}: hazard ratio is under than 1.0).\\
    The 22 gene symbol listed on the side: hazard ratio $> 1.8$ or $< 0.6$.\\
    (X-axis: Kaplan-Meier survival estimates, with \acrshort{fdr}-adjusted \textit{P} value (log10 transformed);
    Y-axis: the hazard ratio (HR) under Cox proportional hazard regression model)
    }
    \label{fig:hazards534}
\end{figure}

>>>>

% strategy should changing; run GCP Rstudio 框列更多的 candidates for GEO (GSE65858) during candidate selection
In the independent test, half genes have p-values less than 0.05, and most of them have p-values $> 0.01$. % table 1 => this is Bonferroni 的結果
Purely based on the number of genes and their p-values, the validation rate is relatively low, and the usability of the biomarkers is questionable. % the validation rate 
The p-values are affected by the sample size, which should be described in the main text. % writing
As I mentioned above, the authors should look for more data to verify these biomarkers. % GEO GSE65858(ok) 
%or even GSE117973? GPL10558	Illumina HumanHT-12 V4.0 expression beadchip; https://www.ncbi.nlm.nih.gov/geo/geo2r/?acc=GSE117973
% Progression-free survival (PFS) is "the length of time during and after the treatment of a disease, such as cancer, that a patient lives with the disease but it does not get worse".[1] In oncology, PFS usually refers to situations in which a tumor is present, as demonstrated by laboratory testing, radiologic testing, or clinically. Similarly, "disease-free survival" is when patients have received treatment and are left with no detectable disease.
% disease-specific survival rate: The percentage of people in a study group who have not died from a specific disease in a defined period of time. The time period usually begins at the time of diagnosis of the disease and ends at the time of death from the disease. 
%Patients who died from causes other than the disease being studied are not counted in this measurement.

@@

% the validation rate
% more GSE datasets; pick-up more candidate (run GCP) in hands 而且要偷看答案
% x using  receiver operating characteristic (ROC) analysis and more GEO datasets
We appreciate the reviewer for the critical comments and thanks for the guidance of our work in cancer research.
% workflow 更加嚴格以增加 validation rate
%Validation rate:\\
%x重新挑選 candidate (FDR100) (GSE2837 and GSE65858)
% => answer is: consensus top3 genes
% (ok) Table 1/2 caption, Fig KP plot: FDR P value (要改為真的FDR) [line 196]
% [2021/06/11]決議;
We have introduced an independent HNSCC cohort (GSE65858, with RNA-Seq expression data) for helping in candidate selection.
%We further
%validate them by using a independent HNSCC cohort (GSE65858, with RNA-Seq expression data)

% problem of it (少 n=30, and RFS only: validation rate 14/100 而且 10% cutoff)
%x Prognoscan (GSE2837) (n=30 less)  RFS only:  10\% cutoff to yield a \textit{P}-value < 0.05.\\
%找出  3 candidates
During our exploration phase with TCGA cohort, the 20 genes, listed
%six overexpressed genes (symbol as CAMK2N1, PGK1, SURF4, USP10, NDFIP1, FOXA2) are bad guy;
%four overexpressed genes (symbol as IL19, FCGBP, IQCN - former symbol as KIAA1683, and NPB) are good guy.
%}
in Figure \ref{fig:hazards3}, have FDR-adjusted \textit{P} values ($<0.001$) in Kaplan-Meier estimate, and survival impact on HR ($> 1.8$ or $< 0.6$) in Cox's model.
%
% [2021/06/13-17]
%CAMK2N1, IL19, and FCGBP is validated by
%candidate_fdr100
%PvalueTex consensus with GSE2837 to yield 3 candidates
In the study of GSE65858 cohort, CAMK2N1, IL19, and FCGBP, keep ahead of the curve by FDR-corrected \textit{P} value ($< 0.05$), and Cox'HR ($>1.8$ or $<0.65$) (please see Table \ref{tab:table_top3_GSE65858} listed below,
% (ok) (FDR KM \textit{P} value) <= # only MSMB KM FDR-adjusted P value = 0.002 
% Consensus 3 genes in Kaplan-Meier survival and Cox's model (dataset: GSE65858)
%Gene.Symbol KM.Pvalue   FDR.KMpvalue    uni_HR  FDR.Pvalue(in TCGA)
%CAMK2N1 0.00687 0.03782500  1.814   1.628308e-05
%FCGBP   0.01020 0.03886709  0.573   4.827833e-05
%IL19    0.03390   0.04738901    0.630   6.543871e-06
%IL19    0.00269  0.03068073 0.630  6.543871e-06
%candidate_fdr100
and also see Figure \ref{fig:hazards534}).
However, the "top rank" of the other 17 genes is replaced by genes such as DUSP6, MSMB, and RBM11.
There is consensus between the TCGA and GSE65858 cohorts that CAMK2N1, IL19, and FCGBP are significant candidates for the biomarker.
%In the consensus of TCGA and GSE65858 cohorts,

%Rplot_GSE65858_CoxHR_CAMK2N1_top3FDRKM.pdf % FDR KM p value of hazards534
% by Validation_GSE65858_survival.R
% Rplot_GSE65858_CoxHR_CAMK2N1_validated.pdf
\begin{figure}
    \centering
    \includegraphics[width=13cm]{Rplot_TCGA_HNSCC_CoxHR_CAMK2N1_top3FDRKM.pdf}
    \bcaption{Volcano plot of genes under survival analyses of TCGA HNSCC.}{
%X axis: unadjusted \textit{P} value of Kaplan-Meier survival (-log10 transformed).
%Y axis: multivariate hazard ratio from Cox proportional regression model.
%Dotted line: significant Bonferroni corrected \textit{P} value. 
%\textcolor{red}{Red dots} mark 10 genes (unvalidated), which impact on poor prognosis ($HR>=1.5$). \textcolor{green}{Green dots} mark 10 genes (unvalidated), which affect on better survival ($HR<=0.5$).
    This cohort has been applied for exploration of the candidate biomarkers.
    Total 9416 genes has \acrshort{fdr}-adjusted \textit{P} value less than 0.05.
    \textcolor{red}{CAMK2N1}, \textcolor{red}{IL19}, \textcolor{red}{FCGBP} and the other 17 genes (marked in \textcolor{black}{black square}) have hazard ratio (HR) $> 1.8$ or $< 0.6$.\\
    Remarks:\\
    \textcolor{red}{Red spots}: $HR > 1.0$;
    \textcolor{green}{Green spots}: $HR < 1.0$;\\
    X-axis: Kaplan-Meier survival estimates, with \acrshort{fdr}-adjusted \textit{P} value (log10 transformed);\\
    Y-axis: HR of Cox proportional hazard regression model\\
    }
    \label{fig:hazards3}
\end{figure}

% Please add the following required packages to your document preamble:
% \usepackage{graphicx}
% Please add the following required packages to your document preamble:
\begin{table}[ht]
\centering
\caption{The consensus between the TCGA and GSE65858 cohorts in Kaplan-Meier survival and Cox's model}
\label{tab:table_top3_GSE65858}
\resizebox{\linewidth}{!}{%
\begin{tabular}{llllclc}
\hline
%\multirow{2}{*}{}
Gene Symbol &
  \multicolumn{2}{c}{KM \textit{P} value} &
  \multicolumn{2}{c}{FDR-adjusted \textit{P} value} &
  \multicolumn{2}{c}{Cox’s univariate HR} \\
%  \hline
 &
  \multicolumn{1}{c}{TCGA} &
  \multicolumn{1}{c}{GSE65858} &
  \multicolumn{1}{c}{TCGA} &
  \multicolumn{1}{c}{GSE65858} &
  \multicolumn{1}{c}{TCGA} &
  \multicolumn{1}{c}{GSE65858} \\
  \hline
  \hline
CAMK2N1 & \num{2.97e-7} & \num{6.87e-3} & \num{1.63e-5} & 0.038 & 2.101 & 1.814 \\
IL19    & n/a           & 0.03          & n/a           & 0.047 & n/a   & 0.630  \\
IL19    & \num{3.73e-7} & \num{2.69e-3} & \num{6.54e-6} & 0.031 & 0.472 & 0.630  \\
FCGBP   & \num{1.21e-6} & 0.01          & \num{4.83e-5} & 0.039 & 0.484 & 0.573\\
\hline
  \multicolumn{7}{l}{(IL19 has two probes in RNA-Seq experiment of GSE65858)}\\
  \multicolumn{7}{l}{(FDR: \acrlong{fdr})}\\
\hline
\end{tabular}%
} % end of \resizebox
\end{table}

@@

\begin{figure}
    \centering
    \includegraphics[width=13cm]{Rplot_GSE65858_CoxHR_CAMK2N1_top3FDRKM.pdf}
    \bcaption{Volcano plot of genes under survival analyses of GSE65858 cohort}{
    % GSE117973 using the same platform GPL10558
    This HNSCC cohort has been applied for filtering of our candidate genes: "CAMK2N1", "IL19" (two probes), and "FCGBP".
    There are 270 HNSCC participants involved in this cohort.
    The number of genes (or probes of RNA-Seq in platform GPL10558, Illumina HumanHT-12 V4.0 expression beadchip) is 30330.
    Total 534 genes has \acrshort{fdr}-adjusted \textit{P} value less than 0.05
    (\textcolor{red}{Red spots}: hazard ratio is greater than 1.0;
    \textcolor{green}{Green spots}: hazard ratio is under than 1.0).\\
    The 22 gene symbol listed on the side: hazard ratio $> 1.8$ or $< 0.6$.\\
    (X-axis: Kaplan-Meier survival estimates, with \acrshort{fdr}-adjusted \textit{P} value (log10 transformed);
    Y-axis: the hazard ratio (HR) under Cox proportional hazard regression model)
    }
    \label{fig:hazards534}
\end{figure}
